\begin{thebibliography}{99}

\bibitem{Abrar-23}
A.~Abrar, A.~S. Che~Mohamed~Arif, and K.~M. Zaini,
``A systematic analysis and review on producer mobility management in named data networks: research background and challenges,''
\textit{Alexandria Engineering Journal},
vol.~69, pp.~785--808, 2023.

\bibitem{Afanasyev-15}
A.~Afanasyev, C.~Yi, L.~Wang, B.~Zhang, and L.~Zhang,
``SNAMP: Secure namespace mapping to scale NDN forwarding,''
in \textit{Proc. IEEE Global Internet Symposium},
Apr. 2015.

\bibitem{Atkinson-12}
R.~Atkinson and S.~Bhatti,
\textit{Identifier-Locator Network Protocol (ILNP) Architectural Description},
IETF RFC 6740, Nov. 2012.

\bibitem{Azgin-14}
A.~Azgin, R.~Ravindran, and G.~Wang,
``Scalable mobility-centric architecture for Named Data Networking,''
in \textit{Proc. IEEE ICCCN}, Aug. 2014, pp.~1--8.

\bibitem{Carofiglio-15}
G.~Carofiglio, G.~Grassi, L.~Muscariello, G.~Pau, and X.~Zeng,
``Experimenting an NDN-based transport protocol for IoT: The case of a smart campus,''
in \textit{Proc. IEEE ICCE-Berlin},
2015, pp.~345--350.

\bibitem{Cheshire-11}
S.~Cheshire, M.~Krochmal, and J.~Wood,
\textit{Understanding Apple’s Back-to-My-Mac (BTMM) Service},
IETF RFC 6281, Jun. 2011.

\bibitem{Dannewitz-09}
C.~Dannewitz,
``NetInf: An information-centric design for the future Internet,''
in \textit{Proc. GI Jahrestagung},
2009.

\bibitem{Farinacci-13}
D.~Farinacci, V.~Fuller, D.~Meyer, and D.~Lewis,
\textit{The Locator/ID Separation Protocol (LISP)},
IETF RFC 6830, Jan. 2013.

\bibitem{Fayyaz-23}
M.~Fayyaz, I.~Shirazi, J.~G. Cedeño, and O.~E. Herrera,
``Information-centric mobile networks: a survey, discussion, and future research directions,''
\textit{IEEE Access},
vol.~11, pp.~40315--40360, 2023.

\bibitem{Grassi-14}
G.~Grassi, D.~Pesavento, G.~Pau, and L.~Zhang,
``VANET via Named Data Networking,''
in \textit{Proc. ACM SIGCOMM Workshop on Information-Centric Networking (ICN)},
2014.

\bibitem{Gundavelli-08}
S.~Gundavelli \textit{et al}.,
\textit{Proxy Mobile IPv6},
IETF RFC 5213, Aug. 2008.

\bibitem{Han-14}
D.~Han, M.~Lee, K.~Cho, T.~T. Kwon, and Y.~Choi,
``Publisher mobility support in content centric networks,''
in \textit{Proc. Intl. Conf. on Information Networking (ICOIN)},
2014, pp.~214--219.

\bibitem{Hermans-12}
F.~Hermans, E.~Ngai, and P.~Gunningberg,
``Global source mobility in the content-centric networking architecture,''
in \textit{Proc. ACM SIGCOMM Workshop on Information-Centric Networking},
2012.

\bibitem{Jacobson-09}
V.~Jacobson, D.~K. Smetters, J.~D. Thornton, M.~F. Plass, N.~H. Briggs, and R.~L. Braynard,
``Networking named content,''
in \textit{Proc. ACM CoNEXT}, 2009, pp.~1--12.

\bibitem{Jacobson-12}
V.~Jacobson, D.~Smetters, N.~Briggs, and R.~Braynard,
``Custodian-based information sharing in vehicular networks,''
\textit{IEEE Communications Magazine},
vol.~50, no.~7, pp.~38--43, 2012.

\bibitem{Jacobson-09b}
V.~Jacobson, D.~K. Smetters, J.~D. Thornton, M.~F. Plass, and N.~H. Briggs,
``VoCCN: voice-over content-centric networks,''
in \textit{Proc. ACM ReArch},
2009, pp.~1--6.

\bibitem{Johnson-04}
D.~Johnson, C.~Perkins, and J.~Arkko,
\textit{Mobility Support in IPv6},
IETF RFC 3775, Jun. 2004.

\bibitem{Kite-18}
Y.~Zhang, H.~Zhang, and L.~Zhang,
``KITE: Producer mobility support in Named Data Networking,''
in \textit{Proc. ACM ICN},
2018, pp.~125--136.

\bibitem{Koponen-07}
T.~Koponen, M.~Chawla, B.-G.~Chun, A.~Ermolinskiy, K.~H.~Kim, S.~Shenker, and I.~Stoica,
``A data-oriented (and beyond) network architecture,''
Proceedings of SIGCOMM 2007,
pp.~181--192, 2007.

\bibitem{Lagutin-10}
D.~Lagutin, K.~Visala, and S.~Tarkoma,
``Publish/subscribe for internet: PSIRP perspective,''
\textit{Towards the Future Internet},
pp.~75--84, 2010.

\bibitem{Lee-12}
J.~Lee, S.~Cho, and D.~Kim,
``Device mobility management in content-centric networking,''
\textit{IEEE Communications Magazine},
vol.~50, no.~12, pp.~28--34, 2012.

\bibitem{Li-13}
D.~Li and M.~C. Chuah,
``SCOM: a scalable content centric network architecture with mobility support,''
in \textit{Proc. IEEE MSN},
2013, pp.~130--137.

\bibitem{Meisel-10}
M.~Meisel, V.~Pappas, and L.~Zhang,
``Ad hoc networking via Named Data,''
in \textit{Proc. ACM MobiArch},
2010, pp.~3--8.

\bibitem{Moskowitz-06}
R.~Moskowitz and P.~Nikander,
\textit{Host Identity Protocol Architecture},
IETF RFC 4423, May 2006.

\bibitem{Naylor-14}
D.~Naylor, M.~K. Mukerjee, S.~Han, H.~Balakrishnan, and C.~W. Chun,
``XIA: architecting a more trustworthy and evolvable Internet,''
\textit{ACM SIGCOMM Computer Communication Review},
vol.~44, no.~3, pp.~50--57, 2014.

\bibitem{Oehlmann-13}
F.~Oehlmann,
``Content-centric networking,''
Network,
vol.~43, pp.~11--18, 2013.

\bibitem{Ramjee-99}
R.~Ramjee, T.~L. Porta, S.~Thuel, K.~Varadhan, and S.~Y. Wang,
``HAWAII: a domain-based approach for IP mobility,''
in \textit{Proc. IEEE ICNP},
1999, pp.~283--292.

\bibitem{Raychaudhuri-12}
D.~Raychaudhuri, K.~Chong, A.~Venkataramani, and P.~Pattnaik,
``MobilityFirst: a robust and trustworthy mobility-centric architecture for the future Internet,''
\textit{ACM SIGMOBILE Mobile Computing and Communications Review},
vol.~16, no.~3, pp.~2--13, 2012.

\bibitem{Soliman-08}
H.~Soliman, C.~Castelluccia, K.~El Malki, and L.~Bellier,
\textit{Hierarchical Mobile IPv6 (HMIPv6) mobility management},
IETF RFC 5380, Oct. 2008.

\bibitem{Snamp-15}
A.~Afanasyev, C.~Yi, L.~Wang, B.~Zhang, and L.~Zhang,
``SNAMP: secure namespace mapping to scale NDN forwarding,''
in \textit{Proc. IEEE Global Internet Symposium},
2015.

\bibitem{Trossen-13}
D.~Trossen and G.~Parisis,
``Designing and realizing an information-centric Internet,''
\textit{IEEE Communications Magazine},
vol.~50, no.~7, pp.~60--67, 2012.

\bibitem{Tyson-12}
G.~Tyson, N.~Sastry, I.~Rimac, R.~Cuevas, and A.~Mauthe,
``A survey of mobility in information-centric networks: challenges and research directions,''
in \textit{Proc. ACM NOM},
2012, pp.~1--6.

\bibitem{Valko-99}
A.~G. Valko,
``Cellular IP: a new approach to Internet host mobility,''
\textit{ACM SIGCOMM Computer Communication Review},
vol.~29, no.~1, pp.~50--65, 1999.

\bibitem{Wang-10}
J.~Wang, R.~Wakikawa, and L.~Zhang,
``DMND: collecting data from mobiles using named data,''
UCLA Tech. Report,
2010.

\bibitem{Wang-13}
L.~Wang, O.~Waltari, and J.~Kangasharju,
``MobiCCN: Mobility support with greedy routing in content-centric networks,''
in \textit{Proc. IEEE Globecom},
2013, pp.~2069--2075.

\bibitem{Xylomenos-14}
G.~Xylomenos, C.~Ververidis, V.~Siris, N.~Fotiou, C.~Tsilopoulos, X.~Vasilakos,
K.~V. Katsaros, and G.~C. Polyzos,
``A survey of information-centric networking research,''
\textit{IEEE Communications Surveys \& Tutorials},
vol.~16, no.~2, pp.~1024--1049, 2014.

\bibitem{Yi-13}
C.~Yi, A.~Afanasyev, I.~Moiseenko, L.~Zhang, and B.~Zhang,
``A case for stateful forwarding plane in Named Data Networking,''
\textit{Computer Communications},
vol.~36, no.~7, pp.~779--791, 2013.

\bibitem{Zeng-18}
X.~Zeng, C.~Westphal, and D.~Raychaudhuri,
``MAP-Me: managing anchor-less producer mobility in content-centric networks,''
\textit{IEEE Trans. Network and Service Management},
vol.~15, no.~2, pp.~596--610, 2018.

\bibitem{Zhang-14}
L.~Zhang, D.~Estrin, J.~Burke, V.~Jacobson, J.~Thornton, G.~Tsudik, and B.~Zhang,
``Named Data Networking,''
\textit{ACM Computer Communication Review},
vol.~44, no.~3, pp.~66--73, 2014.

\bibitem{Zhang-16}
Y.~Zhang, A.~Afanasyev, J.~Burke, and L.~Zhang,
``A survey of mobility support in Named Data Networking,''
in \textit{Proc. IEEE INFOCOM Workshops},
2016, pp.~83--88.

\bibitem{Zhou-14}
Z.~Zhou, X.~Tan, H.~Zhou, and D.~Ma,
``MobiNDN: A mobility support architecture for NDN,''
in \textit{Proc. 33rd Chinese Control Conference (CCC)},
2014, pp.~6784--6789.

\bibitem{Zhu-11}
Z.~Zhu, R.~Wakikawa, and L.~Zhang,
``A survey of mobility support in the Internet,''
IETF RFC 6301, July 2011.

\end{thebibliography}
